### 2020-06-03 writeup/proof_examples.tex
reorg

\section{Supplementary Materials for the Theoretical Implications}

@@

@@

\subsection{Labeled data de-noising}\label{app_proof_data}

In this section, we consider the case where the two tasks may have difference variances $\sigma_1^2\ne \sigma_2^2$ for the noises. In particular, we show Proposition \ref{prop_var_transition}, which gives a transition threshold with respect to the difference between the noise levels of the two tasks.

>>>>

\section{Proofs for Isotropic Settings}

@@

%\subsection{Labeled data de-noising}\label{app_proof_data}

Next we consider the case where the two tasks have different noise variances $\sigma_1^2\ne \sigma_2^2$. In particular, we show Proposition \ref{prop_var_transition}, which gives a transition threshold with respect to the difference between the noise levels of the two tasks.

@@

### 2020-06-03 writeup/proofs_sec3.tex
reorg

\section{Supplementary Materials for the Technical Results}\label{app_proof_sec3}

\subsection{Preliminaries}

\subsubsection{Data models}
First, we give the basic assumption for our main objects---the random matrices $X_i$, $i=1,2$.

@@

\subsubsection{The Multi-Task Learning Estimator} %\label{sec_MTLest}
From \cite{WZR20}, we know that we need to explicitly restrict the capacity $r$ of $B$ so that there is transfer between the two tasks.
for the rest of the section, we shall consider the case of two tasks with $r=1$. 
Then equation \eqref{eq_mtl} simplifies to 
\begin{align}\label{eq_mtl_2task}
	f(B; w_1, w_2) = \bignorm{X_1 B w_1 - Y_1}^2 + \bignorm{X_2 B w_2 - Y_2}^2,
\end{align}
where $B\in\real^p$ and $w_1, w_2$ are both real numbers. To solve the above problem, suppose that $w_1, w_2$ are fixed, by local optimality, we find the optimal $B$ as
\begin{align}
	& \hat{B}(w_1, w_2) = (w_1^2 X_1^{\top}X_1 + w_2^2 X_2^{\top}X_2)^{-1} (w_1 X_1^{\top}Y_1 + w_2 X_2^{\top}Y_2) \label{hatB}\\
	&= \frac{1}{w_2} \left( \frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(\frac{w_1}{w_2} X_1^{\top}Y_1 + X_2^{\top}Y_2\right) \nonumber\\
	&= \frac{1}{w_2}\left[\beta_t + \left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\bigbrace{X_1^{\top}X_1\left(\frac{w_1}{w_2}\beta_1 - \frac{w_1^2}{w_2^2} \beta_2\right) + \left(\frac{w_1}{w_2} X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2\right)}\right]. \nonumber
\end{align}
As a remark, when $w_1 = w_2 = 1$, we recover the linear regression estimator.
The advantage of using $f(B; w_1, w_2)$ is that if $\beta_1$ is a scaling of $\beta_2$, then this case can be solved optimally using equation \eqref{eq_mtl_2task} \cite{KD12}.

@@

\subsubsection{Tools for Random Matrices}
We now state several helper lemmas to get estimates on $L(\hat{\beta}_t^{\STL})$ and $L(\hat{\beta}_t^{\MTL})$. The first lemma, which is a folklore result in random matrix theory, helps to determine the asymptotic limit of $\te(\hat{\beta}_t^{\STL})$, as $p\to \infty$. When the entries of $X$ are multivariate Gaussian, this lemma recovers the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}. For general non-Gaussian random matrices, it can be obtained from Stieltjes transform method; see e.g., Lemma 3.11 of \cite{bai2009spectral}. Here we shall state a result obtained from Theorem 2.4 in \cite{isotropic}, which gives an almost sharp error bound. 
\begin{lemma}\label{lem_minv} 
Suppose $X$ satisfies assumption \ref{assm_secA1}. Let $A$ be any $p\times p$ matrix that is independent of $X$. We have that for any constant $\e>0$,
	\be\label{XXA}  \bigtr{(X^{\top}X)^{-1}A} = \frac{1}{\rho - 1} \frac1p\tr(\Sigma^{-1}A) +\bigo{ \|A\|p^{-1/2+\epsilon}} \ee
with high probability.
\end{lemma}

>>>>

\section{Supplementary Materials for Section \ref{sec_main}}\label{app_proof_sec3}

\subsection{Data Models}\label{app_data_model}
First, we give the basic assumption for our main objects---the random matrices $X_i$, $i=1,2$.

@@

\subsection{The Multi-Task Learning Estimator}\label{sec_MTLest}
From \cite{WZR20}, we know that we need to explicitly restrict the capacity $r$ of $B$ so that there is transfer between the two tasks.
for the rest of the section, we shall consider the case of two tasks with $r=1$. 
Then equation \eqref{eq_mtl} simplifies to 
\begin{align}\label{eq_mtl_2task}
	f(B; w_1, w_2) = \bignorm{X_1 B w_1 - Y_1}^2 + \bignorm{X_2 B w_2 - Y_2}^2,
\end{align}
where $B\in\real^p$ and $w_1, w_2$ are both real numbers. To solve the above problem, suppose that $w_1, w_2$ are fixed, by local optimality, we find the optimal $B$ as
\begin{align}
	& \hat{B}(w_1, w_2) = (w_1^2 X_1^{\top}X_1 + w_2^2 X_2^{\top}X_2)^{-1} (w_1 X_1^{\top}Y_1 + w_2 X_2^{\top}Y_2) \label{hatB}\\
	&= \frac{1}{w_2} \left( \frac{w_1^2}{w_2^2}  X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1} \left(\frac{w_1}{w_2} X_1^{\top}Y_1 + X_2^{\top}Y_2\right) \nonumber\\
	&= \frac{1}{w_2}\left[\beta_t + \left(\frac{w_1^2}{w_2^2} X_1^{\top}X_1 + X_2^{\top}X_2\right)^{-1}\bigbrace{X_1^{\top}X_1\left(\frac{w_1}{w_2}\beta_1 - \frac{w_1^2}{w_2^2} \beta_2\right) + \left(\frac{w_1}{w_2} X_1^{\top}\varepsilon_1 + X_2^{\top}\varepsilon_2\right)}\right]. \nonumber
\end{align}
As a remark, when $w_1 = w_2 = 1$, we recover the linear regression estimator.
The advantage of using $f(B; w_1, w_2)$ is that if $\beta_1$ is a scaling of $\beta_2$, then this case can be solved optimally using equation \eqref{eq_mtl_2task} \cite{KD12}.

@@

\subsection{Concentration Bounds}\label{app_tool}
We now state several helper lemmas to get estimates on $L(\hat{\beta}_t^{\STL})$ and $L(\hat{\beta}_t^{\MTL})$. The first lemma, which is a folklore result in random matrix theory, helps to determine the asymptotic limit of $\te(\hat{\beta}_t^{\STL})$, as $p\to \infty$. When the entries of $X$ are multivariate Gaussian, this lemma recovers the classical result for the mean of inverse Wishart distribution \cite{anderson1958introduction}. For general non-Gaussian random matrices, it can be obtained from Stieltjes transform method; see e.g., Lemma 3.11 of \cite{bai2009spectral}. Here we shall state a result obtained from Theorem 2.4 in \cite{isotropic}, which gives an almost sharp error bound. 
\begin{lemma}\label{lem_minv} 
Suppose $X$ satisfies assumption \ref{assm_secA1}. Let $A$ be any $p\times p$ matrix that is independent of $X$. We have that for any constant $\e>0$,
	\be\label{XXA}  \bigtr{(X^{\top}X)^{-1}A} = \frac{1}{\rho - 1} \frac1p\tr(\Sigma^{-1}A) +\bigo{ \|A\|p^{-1/2+\epsilon}} \ee
with high probability.
\end{lemma}
